
\subsection*{Installing the research app on your mobile phone}
\Callout{App install}{%
You can install the research app on your mobile phone by scanning the QR code or link below.
\begin{itemize}
    \item \textbf{iOS:} link / QR code (to be added)
    \item \textbf{Android:} link / QR code (to be added)
\end{itemize}

Alternatively, I can install the app on your phone directly by connecting to my laptop, if we are able to meet in person.  

\subsection*{Scheduling start and end dates}
We can schedule a time for you to attend an onboarding session to install the app and get started. This will be a 30 minute session where we will go through the app and how to use it.

The session can be held online or in person, depending on your preference.

During this session, we will also schedule an end date session to complete the participation questionnaires.

\subsection*{Getting started}
We will go through the app together at our first meeting.

Should you wish to familiarise yourself with the app before our first meeting some walkthroughs are included below.

\subsection{First Launch}
When you first launch the app, you will be prompted to grant permissions to the app.
\subsesction{Tracking tab}
\subsubection{Setting your device ID}
You will need to enter your unique device ID which I will provide when we meet.
\subsubsection{Setting your home location}
\subsection{Tracking tab}
\subsection{Diary tab}
\subsubsection*{Selecting a day}
\subsubsection*{Filling in and submitting the diary}